`r if(knitr:::is_latex_output()) '\\appendix'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'` 

<!--
If you feel it necessary to include an appendix, it goes here.
-->


# Autoimpute References

`Autoimpute` is an open-source Python package distributed under the MIT license. The package is hosted on github and registered with the official Python Package Index. The authors also host a website that explores Autoimpute in more detail and provides in-depth tutorials on how end-users can get the most out of the package. The table below provides links to the package and the author's website.

```{r appendixa, echo=FALSE, warning=FALSE}
text_tbl <- data.frame(
  Source = c("Github", "PyPI", "Website"),
  Link = c(
    "https://github.com/kearnz/autoimpute",
    "https://pypi.org/project/autoimpute/",
    "https://kearnz.github.io/autoimpute-tutorials/"
  )
)

kable(text_tbl, caption="Autoimpute Sources", booktabs=TRUE, escape=FALSE) %>%
  kable_styling(position="left", full_width=TRUE, latex_options="hold_position") %>%
  row_spec(0, bold=TRUE, font_size=13) %>%
  column_spec(1, width="5em")
```

# Notation Cheatsheet

```{r appendixbnotation, echo=FALSE, warning=FALSE}
text_tbl <- data.frame(
  Notation = c(
    "$n$",
    "$p$",
    "$Y$",
    "$Y_{obs}$",
    "$Y_{mis}$",
    "$y_{ij}$",
    "$R$",
    "$r_{ij}$",
    "$\\psi$"),
  Description = c(
    "The number of records or observations in a matrix",
    "The number of columns or features in a matrix",
    "The complete data matrix of observed and missing records",
    "Records within $Y$ that are completely observed for all columns $p$",
    "Records within $Y$ with a missing value in any column in $p$",
    "A scalar value $y$ in row $i$ and column $j$ of matrix $Y$",
    "The missing indicator matrix, where each value $r_{ij} \\in 0,1$",
    "A scalar value $r$ in row $i$ and column $j$ of matrix $R$",
    "The parameters of the missing data model"
  )
)

kable(text_tbl, caption ="Notation", booktabs=TRUE, escape=FALSE) %>%
  kable_styling(position="left", full_width=TRUE, latex_options="hold_position") %>%
  row_spec(0, bold=TRUE, font_size=13) %>%
  column_spec(1, width="5em")
```

# Expression Cheatsheet

```{r appendixcexpressions, echo=FALSE, warning=FALSE}

text_tbl <- data.frame(
  Expression = c(
    "$Y = (Y_{mis}, Y_{obs})$",
    "$r_{ij} = 0$",
    "$r_{ij} = 1$",
    "$P(R\\mid Y_{obs}, Y_{mis},\\psi)$",
    "$P(R=0\\mid Y_{obs},Y_{mis},\\psi) = P(R=0\\mid \\psi)$",
    "$P(R=0\\mid Y_{obs},Y_{mis},\\psi) = P(R=0\\mid Y_{obs}, \\psi)$",
    "$P(Y_{mis}\\mid Y_{obs}, R)$",
    "$P(Y\\mid Y_{obs}, R=1) = P(Y\\mid Y_{obs}, R=0)$"
    ),
  Description = c(
    "The complete data matrix equals the conjoined observed and missing data matrices",
    "When a value $r_{ij}=0$, the corresponding value $y_{ij}$ is missing",
    "When a value $r_{ij}=1$, the corresponding value $y_{ij}$ is observed",
    "General expression for a missing data model. Also the form for MNAR, which does not reduce",
    "The reducible form of the missing data model under MCAR",
    "The reducible form of the missing data model under MAR",
    "General expression for an imputation model",
    "If ignorability holds, missing and observed data come from the same underlying distribution. Under this condition, imputation models can safely ignore $\\psi$"
  )
)

kable(text_tbl, caption="Expressions", booktabs=TRUE, escape=FALSE) %>%
  kable_styling(position="left", full_width=TRUE, latex_options="hold_position") %>%
  row_spec(0, bold=TRUE, font_size=13)
```


# Concepts Related to Missingness

```{r appendixdconcepts, echo=FALSE, warning=FALSE}

text_tbl <- data.frame(
  Concept = c(
    "complete data matrix",
    "missing indicator matrix",
    "missing data mechanism",
    "missing data model",
    "missing completely at random (MCAR)",
    "missing at random (MAR)",
    "missing not at random (MNAR)",
    "ignorability",
    "missing data method",
    "deletion",
    "imputation model"
    ),
  Definition = c(
    "The complete matrix $Y$, which is comprised of both observed and unobserved records",
    "The missing indicator $R$, which indicates which values in $Y$ are missing or not",
    "Process that governs the relationship between observe data and probability of missingness",
    "General expression that formalizes the relationship specified by the missing data mechanism",
    "A missing data mechanism in which missingness depends on $\\psi$ only",
    "A missing data mechanism in which missingness depends on $Y_{obs}$ and $\\psi$ only",
    "A missing data mechanism in which missingness depends on $Y_{obs}$, $Y_{mis}$, and $\\psi$",
    "A set of criteria required for imputation models to safely ignore the parameters of the missing data model $\\psi$. MAR and MCAR are considered ignorable",
    "A method used to handle missing data. The two types of missing data methods are deletion and imputation",
    "A missing data method by which records with any missing observations are discarded from the dataset. Deletion is generally synonymous with listwise deletion or complete case analysis. The terms are used interchangeably to refer to deletion methods",
    "An missing data method by which missing values in a dataset are replaced with plausible imputations from an imputation model"
  )
)

kable(text_tbl, caption="Concepts", booktabs=TRUE, escape=FALSE) %>%
  kable_styling(position="left", full_width=TRUE, latex_options="hold_position") %>%
  row_spec(0, bold=TRUE, font_size=13) %>%
  column_spec(1, width="20em")
```

# Univariate Imputation Methods

# Multivariate Imputation Methods

# Analysis Models and Diagnostics