`r if(knitr:::is_latex_output()) '\\appendix'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'` 

<!--
If you feel it necessary to include an appendix, it goes here.
-->


# Autoimpute References

`Autoimpute` is an open-source Python package distributed under the MIT license. The package is hosted on github and registered with the official Python Package Index. The authors also host a website that explores Autoimpute in more detail and provides in-depth tutorials on how end-users can get the most out of the package. The table below provides links to the package and the author's website.

```{r appendixa, echo=FALSE, warning=FALSE}
text_tbl <- data.frame(
  Source = c("Github", "PyPI", "Website"),
  Link = c(
    "https://github.com/kearnz/autoimpute",
    "https://pypi.org/project/autoimpute/",
    "https://kearnz.github.io/autoimpute-tutorials/"
  )
)

kable(text_tbl, caption = "Autoimpute Sources", escape = FALSE) %>%
  kable_styling(latex_options = "hold_position")
```

# Notation Cheatsheet

#### Notations {.unnumbered}

```{r appendixbnotation, echo=FALSE, warning=FALSE}
text_tbl <- data.frame(
  Source = c(
    "$n$",
    "$p$",
    "$Y$",
    "$Y_{obs}$",
    "$Y_{mis}$",
    "$y_{ij}$",
    "$R$",
    "$r_{ij}$",
    "$\\psi$"),
  Link = c(
    "The number of records or observations in a matrix",
    "The number of columns or features in a matrix",
    "The complete data matrix of observed and missing records",
    "Records within $Y$ that are completely observed for all columns $p$",
    "Records within $Y$ with a missing value in any column in $p$",
    "A scalar value $y$ in row $i$ and column $j$ of matrix $Y$",
    "The missing indicator matrix, where each value $r_{ij} \\in 0,1$",
    "A scalar value $r$ in row $i$ and column $j$ of matrix $R$",
    "The parameters of the missing data model"
  )
)

kable(text_tbl, caption = "Notation", escape=FALSE) %>%
  kable_styling(latex_options = "hold_position")
```

#### Expressions {.unnumbered}

```{r appendixbexpressions, echo=FALSE, warning=FALSE}

text_tbl <- data.frame(
  Source = c(
    "$Y = (Y_{mis}, Y_{obs})$",
    "$r_{ij} = 0$",
    "$r_{ij} = 1$",
    "$P(R\\mid Y_{obs}, Y_{mis},\\psi)$",
    "$P(R=0\\mid Y_{obs},Y_{mis},\\psi) = P(R=0\\mid \\psi)$",
    "$P(R=0\\mid Y_{obs},Y_{mis},\\psi) = P(R=0\\mid Y_{obs}, \\psi)$",
    "$P(Y_{mis}\\mid Y_{obs}, R)$",
    "$P(Y\\mid Y_{obs}, R=1) = P(Y\\mid Y_{obs}, R=0)$"
    ),
  Link = c(
    "The complete data matrix equals the conjoined observed and missing data matrices",
    "When a value $r_{ij}=0$, the corresponding value $y_{ij}$ is missing",
    "When a value $r_{ij}=1$, the corresponding value $y_{ij}$ is observed",
    "General expression for a missing data model. Also the form for MNAR, which does not reduce",
    "The reducible form of the missing data model under MCAR",
    "The reducible form of the missing data model under MAR",
    "General expression for an imputation model",
    "If ignorability holds, missing and observed data come from the same underlying distribution. Under this condition, imputation models can safely ignore $\\psi$"
  )
)

kable(text_tbl, caption = "Expressions", escape = FALSE) %>%
  kable_styling(latex_options = "hold_position")
```


# Concepts Related to Missingness

| Concept                             | Definition                                                           
| :---------------------------------- | :---------------------------------------------------------------------------------------------------------------
| complete data matrix                | The complete matrix $Y$, which is comprised of both observed and unobserved records
| missing indicator matrix            | The missing indicator $R$, which indicates which values in $Y$ are missing or not
| missing data mechanism              | Process that governs the relationship between observe data and probability of missingness
| missing data model                  | General expression that formalizes the relationship specified by the missing data mechanism
| missing completely at random (MCAR) | A missing data mechanism in which missingness depends on $\psi$ only
| missing at random (MAR)             | A missing data mechanism in which missingness depends on $Y_{obs}$ and $\psi$ only
| missing not at random (MNAR)        | A missing data mechanism in which missingness depends on $Y_{obs}$, $Y_{mis}$, and $\psi$
| ignorability                        | A set of criteria required for imputation models to safely ignore the parameters of the missing data model $\psi$. MAR and MCAR are considered ignorable
| imputation model                    | An algorithm used to replace missing values in a dataset with plausible imputations

# Univariate Imputation Methods

# Multivariate Imputation Methods

# Analysis Models and Diagnostics