`r if(knitr:::is_latex_output()) '\\appendix'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'` 

<!--
If you feel it necessary to include an appendix, it goes here.
-->


# Autoimpute References

`Autoimpute` is an open-source Python package distributed under the MIT license. The package is hosted on github and registered with the official Python Package Index. The authors also host a website that explores Autoimpute in more detail and provides in-depth tutorials on how end-users can get the most out of the package. The table below provides links to the package and the author's website.

```{r appendixa, echo=FALSE, warning=FALSE}
text_tbl <- data.frame(
  Source = c("Github", "PyPI", "Website"),
  Link = c(
    "https://github.com/kearnz/autoimpute",
    "https://pypi.org/project/autoimpute/",
    "https://kearnz.github.io/autoimpute-tutorials/"
  )
)

kable(text_tbl, caption="Autoimpute Sources", booktabs=TRUE, escape=FALSE) %>%
  kable_styling(position="left", full_width=TRUE, latex_options="hold_position") %>%
  row_spec(0, bold=TRUE, font_size=13) %>%
  column_spec(1, width="5em")
```

# Missingness Notation Cheatsheet

```{r appendixbnotation, echo=FALSE, warning=FALSE}
text_tbl <- data.frame(
  Notation = c(
    "$n$",
    "$p$",
    "$Y$",
    "$Y_{obs}$",
    "$Y_{mis}$",
    "$y_{ij}$",
    "$R$",
    "$r_{ij}$",
    "$\\psi$",
    "$m$",
    "$I_j$",
    "$O_j$",
    "$Q$",
    "$\\hat Q$",
    "$U$",
    "$\\hat U$",
    "$\\bar Q$",
    "$\\bar U$",
    "$B$",
    "$T$"
    ),
  Description = c(
    "The number of records or observations in a matrix",
    "The number of columns or features in a matrix",
    "The complete data matrix of observed and missing records",
    "Records within $Y$ that are completely observed for all columns $p$",
    "Records within $Y$ with a missing value in any column in $p$",
    "A scalar value $y$ in row $i$ and column $j$ of matrix $Y$",
    "The missing indicator matrix, where each value $r_{ij} \\in 0,1$",
    "A scalar value $r$ in row $i$ and column $j$ of matrix $R$",
    "The parameters of the missing data model",
    "The number of complete datasets $Y$ to impute independently",
    "The influx coefficient",
    "The outflux coefficient",
    "The population parameter of scientific interest",
    "The estimate for $Q$ using hypothetically complete data",
    "The variance-covariance matrix of $Q$",
    "The variance-covariance matrix of estimate $\\hat Q$",
    "The pooled parameter estimate of $Q$ under multiple imputation",
    "The variance-within under multiple imputation",
    "The variance-between under multiple imputation",
    "The total variance under multiple imputation"
  )
)

kable(text_tbl, caption ="Notation", booktabs=TRUE, escape=FALSE) %>%
  kable_styling(position="left", full_width=TRUE, latex_options="hold_position") %>%
  row_spec(0, bold=TRUE, font_size=13) %>%
  column_spec(1, width="5em")
```

# Missingess Expression Cheatsheet

```{r appendixcexpressions, echo=FALSE, warning=FALSE}

text_tbl <- data.frame(
  Expression = c(
    "$Y = (Y_{mis}, Y_{obs})$",
    "$r_{ij} = 0$",
    "$r_{ij} = 1$",
    "$P(R\\mid Y_{obs}, Y_{mis},\\psi)$",
    "$P(R=0\\mid Y_{obs},Y_{mis},\\psi) = P(R=0\\mid \\psi)$",
    "$P(R=0\\mid Y_{obs},Y_{mis},\\psi) = P(R=0\\mid Y_{obs}, \\psi)$",
    "$P(Y_{mis}\\mid Y_{obs}, R)$",
    "$P(Y\\mid Y_{obs}, R=1) = P(Y\\mid Y_{obs}, R=0)$",
    "$I_j = \\frac{\\sum_j^p\\sum_k^p\\sum_i^n (1-r_{ij})r_{ik}}{\\sum_k^p\\sum_i^n r_{ik}}$",
    "$O_j = \\frac{\\sum_j^p\\sum_k^p\\sum_i^n r_{ij}(1-r_{ik})}{\\sum_k^p\\sum_i^n 1-r_{ij}}$",
    "$E(\\hat Q|Y) = Q$",
    "$\\bar Q = \\frac{1}{m}\\sum_{\\ell=1}^m \\hat Q_\\ell$",
    "$\\bar U = \\frac{1}{m}\\sum_{\\ell=1}^m \\bar U_\\ell$",
    "$B = \\frac{1}{m-1}\\sum_{\\ell=1}^m (\\hat Q_\\ell-\\bar Q)(\\hat Q_\\ell-\\bar Q)'$",
    "$T = \\bar U + B + \\frac{B}{m}$"
    ),
  Description = c(
    "The complete data matrix equals the conjoined $Y_{obs}$ and $Y_{mis}$",
    "When a value $r_{ij}=0$, the corresponding value $y_{ij}$ is missing",
    "When a value $r_{ij}=1$, the corresponding value $y_{ij}$ is observed",
    "General expression for a missing data model. Also form for MNAR",
    "Reducible form of the missing data model under MCAR",
    "Reducible form of the missing data model under MAR",
    "General expression for an imputation model",
    "Implication of ignorability in which imputation models can safely ignore $\\psi$",
    "The forumla for influx coefficient",
    "The formula for outflux coefficient",
    "The equality necessary for unbiasedness of an estimate $\\hat Q$ conditional on $Y$",
    "The pooled estimate for $Q$ is the mean of $m$ $\\hat Q$ estimates from $m$ imputations",
    "The variance within is the mean of the $m$ $\\hat U$ estimates from $m$ imputations",
    "The variance between is the additional variance in estimating $\\hat Q$ during $m$ imputations",
    "The total variance is the sum of variance within, variance between, and added variance from finite number of imputations $m$"
  )
)

kable(text_tbl, caption="Expressions", booktabs=TRUE, escape=FALSE) %>%
  kable_styling(position="left", full_width=TRUE, latex_options="hold_position") %>%
  row_spec(0, bold=TRUE, font_size=13)
```


# Concepts Related to Missingness

```{r appendixdconcepts, echo=FALSE, warning=FALSE}

text_tbl <- data.frame(
  Concept = c(
    "complete data matrix",
    "missing indicator matrix",
    "missing data mechanism",
    "missing data model",
    "MCAR",
    "MAR",
    "MNAR",
    "ignorability",
    "missing data method",
    "deletion",
    "imputation model",
    "analysis model",
    "target",
    "univariate",
    "multivariate",
    "missing data pattern",
    "single imputation",
    "multiple imputation",
    "influx",
    "outflux",
    "pooled parameter estimate",
    "variance within",
    "variance between",
    "total variance"
    ),
  Definition = c(
    "The complete matrix $Y$, which is comprised of $Y_{obs}$ and $Y_{mis}$",
    "Missing indicator $R$ suggests which values in $Y$ are missing",
    "Process that governs relationship b/w observed and $P(missing)$",
    "Formalizes relationship specified by missing data mechanism",
    "Missing data mechanism depends on $\\psi$ only",
    "Missing data mechanism depends on $Y_{obs}$ and $\\psi$ only",
    "Missing data mechanism depends on $Y_{obs}$, $Y_{mis}$, and $\\psi$",
    "Criteria required for imputation models to ignore $\\psi$",
    "Method used to handle missing data. Use deletion or imputation",
    "Discard missing values from the dataset",
    "Replace missing values with imputations from imputation model",
    "A supervised machine learning model applied to imputed data",
    "Column with missing values to be imputed",
    "Models using target to determine imputation for target",
    "Models using features to predict imputed values for target",
    "Pattern suggesting information transferrable b/w variables",
    "Impute missing values once prior to analysis",
    "Impute missing values $m$ times prior to analysis",
    "Candidates to be imputed using the other predictors",
    "Variables useful as predictors to impute a target variable",
    "The coefficients of an analysis model under multiple imputation",
    "The average of the variance of the parameter estimate from each imputation",
    "The variance introduced from different parameter estimates across imputations",
    "The accurate representation of variance under multiple imputation"
  )
)

kable(text_tbl, caption="Concepts", booktabs=TRUE, escape=FALSE) %>%
  kable_styling(position="left", full_width=TRUE, latex_options="hold_position") %>%
  row_spec(0, bold=TRUE, font_size=13)  %>%
  column_spec(1, width="10em")
```

# Univariate Imputation Methods

# Multivariate Imputation Methods

# Analysis Models and Diagnostics